OptiFit GLNE Exploratory

### 2021-07-02 exploratory/exploratory.Rmd

fraction_mapped %>% 
  ggplot(aes(x=fraction_mapped)) + 
    geom_histogram(fill="grey",color="black") +
  theme_bw() + 
  scale_x_continuous(labels=scales::percent) +
  xlab("Percent of reads mapped with cluster.fit") +
  ylab("number of samples")

@@

#mcc_data$type <- factor(mcc_data$type,levels=c("OptiClust_all","OptiClust_489","OptiFit_1"))
mcc_data %>% 
  ggplot(aes(x=type,y=mcc,color=type)) + 
    geom_jitter(height=0) +
    xlab("") +
    theme_bw()

>>>>

med <- median(fraction_mapped$fraction_mapped)
med_frac <- paste0(100*median(fraction_mapped$fraction_mapped),"%")
min_frac <- paste0(100*min(fraction_mapped$fraction_mapped),"%")
max_frac <- paste0(100*max(fraction_mapped$fraction_mapped),"%")

fraction_mapped %>% 
  ggplot(aes(x=fraction_mapped)) + 
    geom_histogram(fill="grey",color="black") +
  theme_bw() + 
  scale_x_continuous(labels=scales::percent) +
  xlab("Percent of reads mapped with cluster.fit") +
  ylab("number of samples") +
  geom_vline(xintercept = med,lty="dashed",lwd=1) +
  annotate("text", x=.90, y=55, label= paste0("Median: ",med_frac)) +   
  annotate("text", x=.90, y=50, label= paste0("Max: ",max_frac)) +
  annotate("text", x=.90, y=45, label= paste0("Min: ",min_frac))

@@

#mcc_data$type <- factor(mcc_data$type,levels=c("OptiClust_all","OptiClust_489","OptiFit_1"))
mcc_data %>% 
  ggplot(aes(x=type,y=mcc,color=type)) + 
    geom_jitter(height=0,size=3,alpha=0.6) +
    xlab("") +
    theme_bw() +
    stat_summary(fun=median,geom="crossbar",color="black",lwd=0.3)
